### 2009-04-06 talk/icooolps2009-dotnet/intro.tex
fix an XXX

Writing a compiler that targets a high CLI or JVM is easier than targeting a real CPU, but
it still requires a lot of work, as
IronPython\footnote{http://www.codeplex.com/IronPython},
Jython\footnote{http://www.jython.org/}
and JRuby\footnote{http://jruby.codehaus.org/} demonstrate.

Moreover, writing a static compiler is often not enough to get high
performance.  IronPython and JRuby are going in the direction of
compiling just-in-time (JIT) specialized versions of the code depending
on the actual values/types seen at runtime; this approach seems to work,
but writing it manually requires an enormous effort.

@@

\anto{XXX: we first say that IronPython\&co. does JIT compilation, then we say
  we are the first to do JIT layering.  This seems a bit strange, though at
  the moment I can't think of any better way to word this concept}

>>>>

Writing a compiler that targets the CLI or JVM is easier than targeting a real CPU, but
it still requires a lot of work, as
IronPython\footnote{http://www.codeplex.com/IronPython},
Jython\footnote{http://www.jython.org/}
and JRuby\footnote{http://jruby.codehaus.org/} demonstrate.

Moreover, writing a static compiler is often not enough to get high
performance.  IronPython and Jython compile code lazily to save memory, but
since they do not exploit the extra information potentially available at
runtime, it is more a delayed static compilation than a true JIT one.
\anto{XXX: someone review the english of the last paragraph, please :-)}

@@
